---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 1"
author: "Insert your name here"
date: "Insert date here"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(readr)
library(dsbox) 
```

```{r load-data, message = FALSE}
states <- read_csv("states.csv")
```

### Exercise 1

```{r}
## Number of rows
num_rows_dennys <- nrow(dennys)
num_rows_dennys
## Number of columns
num_col_dennys <- ncol(dennys)
num_col_dennys

## Each of rows represent a different locaton/address

## The variables are city, state, zip, longitude, latitude
```

### Exercise 2

```{r}
## Number of rows
num_rows_laq <- nrow(laquinta)

## Number of columns
num_col_laq <- ncol(laquinta)
num_rows_laq
num_col_laq

```
Each of rows represent a different location/address

The variables are city, state, zip, longitude, latitude

### Exercise 3
LaQuinta has locations in Canada, Mexico, New Zealand, Honduras, Turkey, UAE, Chile, and Columbia. 

Denny's has locations in Chile, Canada, Mexico, Costa Rica, Honduras, El Salvador, United Kingdom, New Zealand, Curacao, China, Dominican Republic, Japan and Guam. 
...

### Exercise 4
we can do a filter everything except the 50 states.

...

### Exercise 5
```{r}
dennys %>%
  filter(!(state %in% states$abbreviation))
```

...

### Exercise 6
```{r}
dennys %>%
  mutate(country = "United States")
```

...

### Exercise 7
```{r}
laquinta %>%
  filter(!(state %in% states$abbreviation))
```
They are in Mexico, Columbia, Canada, and Honduras.
...

### Excercise 8
```{r eval = FALSE}
laquinta <- laquinta %>%
  mutate(country = case_when(
    state %in% state.abb     ~ "United States",
    state %in% c("ON", "BC") ~ "Canada",
    state == "ANT"           ~ "Colombia",
    state == "FM"            ~ "Honduras",
    state %in% c("SL","PU","AG","QR","CH","NL","VE") ~ "Mexico"
  ))
```

```{r}
laquinta <- laquinta %>%
  filter(country == "United States")
```
...

### Exercise 9
```{r}
dennys <- dennys %>%
  count(state) %>%
  inner_join(states, by = c("state" = "abbreviation"))
```
...

### Exercise 10
```{r}
dennys <- dennys %>%
  mutate(establishment = "Denny's")

laquinta <- laquinta %>%
  mutate(establishment = "La Quinta")

dn_lq <- bind_rows(dennys, laquinta)

ggplot(dn_lq, mapping = aes(x = longitude, y = latitude, color = establishment, alpha = 0.3)) +
  geom_point()
```
### Exercise 11
```{r}
dn_lq_nc <- dn_lq %>%
  filter(state == "NC")
dn_lq_nc

ggplot(dn_lq_nc, mapping = aes(x = longitude, y = latitude, color = establishment, alpha = 0.5)) +
  geom_point()
```
...
### Exercise 12
```{r}
dn_lq_tx <- dn_lq %>%
  filter(state == "TX")
dn_lq_tx

ggplot(dn_lq_tx, mapping = aes(x = longitude, y = latitude, color = establishment, alpha = 0.5)) +
  geom_point()
```

Add exercise headings as needed.
